\section{Context}

RTS game provide a very interesting baseground for developping and testing multi-agent cooperative behavior.
Our goal was to create an AI for the \texttt{Stacraft: Broodwar} game. We focused only on the military aspect of the game. Therefore, our bots do not handle harvesting ressources, build order, troops production, \ldots.

We only dealt with the following scenario: Two teams fight against each other with the same number of units. The goal is to destroy all ennemies units.
This restriction was made in order to test and compare different micro-management algorithm. 
At the current time, we have the following bots:
\begin{shortitem}
\item \texttt{AC: Attack Closest} All units attack their closest opponent,
\item \texttt{ACL: Attack Closest Lethal} All units attack the closest opponent that will not die soon (\emph{i.e} If the amount of damage attributed to this unit is not already enough to kill him soon),
\item \texttt{KS: Kiting Strategy} All units attack their closest opponent applying a kiting strategy,
\item \texttt{KSL: Kiting Strategy Lethal} All units attack the closest opponent that will not die soon applying a kiting strategy,
\item \texttt{GB: Graph Bot} Heuristic search in the game graph to compute the cleverest action.
\end{shortitem}

\begin{definition}[Scripted based behaviors]
Make decision only on a reactive way and do not make any plan for the future of the game. (Bots \texttt{AC, ACL, KS, KSL})
\end{definition}

\begin{definition}[Heuristic based behaviors]
% TODO
blabla \ldots
\end{definition}
